\thetitle

### 2008-06-29 figures/basic_behaviors.tex
Fixed pie charts.
Changes for auto publication.

\begin{sidewaysfigure*}
{\includegraphics[height=5.95in]{basic_behaviors_1.pdf}}\hfill%
{\includegraphics[height=5.95in]{basic_behaviors_2.pdf}}
\caption{%
The ten most prevalent components of flow behavior as pairs of packet payload size and of inter-packet interval distributions.
The distributions are shown as cumulative distribution functions: the $x$-axis represents payload size (in kilobytes) or inter-packet interval duration (in log-seconds, base 10), respectively;
the $y$-axis indicates the probability a value occurring, less than or equal to the $x$ value.
The behaviors are ordered in descending rank of how many packets they explain;
to the left, each behavior's rank is indicated, together with the percentage of total packets associated with it, and the cumulative percentage of packets explained.
To the right of each behavior is a pie chart showing the breakdown of associated packets by protocol, as determined by well-known port numbers.
}
\label{fig:basic-behaviors}
\end{sidewaysfigure*}

>>>>

\begin{sidewaysfigure*}
{\includegraphics[height=5.95in]{basic_behaviors_1}}\hfill%
{\includegraphics[height=5.95in]{basic_behaviors_2}}
\caption{%
The ten most prevalent components of flow behavior as pairs of packet payload size and of inter-packet interval distributions.
The distributions are shown as cumulative distribution functions: the $x$-axis represents payload size (in kilobytes) or inter-packet interval duration (in log-seconds, base 10), respectively;
the $y$-axis indicates the probability a value occurring, less than or equal to the $x$ value.
The behaviors are ordered in descending rank of how many packets they explain;
to the left, each behavior's rank is indicated, together with the percentage of total packets associated with it, and the cumulative percentage of packets explained.
To the right of each behavior is a pie chart showing the breakdown of associated packets by protocol, as determined by well-known port numbers.
Pie slices are only labeled if they constitute at least 3\% of associated packets.
}
\label{fig:basic-behaviors}
\end{sidewaysfigure*}

### 2008-06-29 figures/box_plots.tex
Changes for auto publication.

\begin{sidewaysfigure*}
\subfloat[\textbf{Application:} Average End-to-End Delay]%
{\includegraphics[width=4.5in]{Application/delay.pdf}}\hfill
\subfloat[\textbf{Application:} Packet Delivery Ratio]%
{\includegraphics[width=4.5in]{Application/delivery_ratio.pdf}}
%
\subfloat[\textbf{Application:} Average Received Throughput]%
{\includegraphics[width=4.5in]{Application/throughput.pdf}}\hfill
\subfloat[\textbf{Network:} AODV Control Overhead]%
{\includegraphics[width=4.5in]{Network/control_packets.pdf}}
%
\subfloat[\textbf{Network:} Packets Dropped in Routing Queue]%
{\includegraphics[width=4.5in]{Network/dropped.pdf}}\hfill
\subfloat[\textbf{Link:} 802.11 Control Overhead]%
{\includegraphics[width=4.5in]{Link/overhead.pdf}}%
%
\caption{%
Box-and-whisker plots of log-ratio error values for all metrics and traffic models.
The lower axis indicates the log-ratio, while the upper axis shows raw ratio values.
Each box contains the central majority of log-ratio values:
the left and right bounds are at the $25^\text{th}$ and $75^\text{th}$ percentiles.
The dark middle line indicates the median value, while the diamond marks the mean.
The whiskers (dotted lines) extend to the furthest non-outlier values, while the points beyond that are outliers. The notch in the middle of each bar indicates a $95\%$ confidence interval for the true underlying median value;
if two notches do not overlap, they are very unlikely to have the same median.
}
\label{fig:box-plots}
\end{sidewaysfigure*}

>>>>

\begin{sidewaysfigure*}
\subfloat[\textbf{Application:} Average End-to-End Delay]%
{\includegraphics[width=4.5in]{Application/delay}}\hfill
\subfloat[\textbf{Application:} Packet Delivery Ratio]%
{\includegraphics[width=4.5in]{Application/delivery_ratio}}
%
\subfloat[\textbf{Application:} Average Received Throughput]%
{\includegraphics[width=4.5in]{Application/throughput}}\hfill
\subfloat[\textbf{Network:} AODV Control Overhead]%
{\includegraphics[width=4.5in]{Network/control_packets}}
%
\subfloat[\textbf{Network:} Packets Dropped in Routing Queue]%
{\includegraphics[width=4.5in]{Network/dropped}}\hfill
\subfloat[\textbf{Link:} 802.11 Control Overhead]%
{\includegraphics[width=4.5in]{Link/overhead}}%
%
\caption{%
Box-and-whisker plots of log-ratio error values for all metrics and traffic models.
The lower axis indicates the log-ratio, while the upper axis shows raw ratio values.
Each box contains the central majority of log-ratio values:
the left and right bounds are at the $25^\text{th}$ and $75^\text{th}$ percentiles.
The dark middle line indicates the median value, while the diamond marks the mean.
The whiskers (dotted lines) extend to the furthest non-outlier values, while the points beyond that are outliers. The notch in the middle of each bar indicates a $95\%$ confidence interval for the true underlying median value;
if two notches do not overlap, they are very unlikely to have the same median.
}
\label{fig:box-plots}
\end{sidewaysfigure*}
